{\includegraphics[width=3cm, height=2.5cm]{Cran.jpg}} \\ \includegraphics[width=7cm, height=1cm]{TB.jpg} \\ {Technical Documentation for TersectBrowser+}

### 2025-05-05 TechDoc/TechDoc.tex
Includes some additional changes to the Introduction/Overview section

\author{David Oluwasusi, Tanya Stead, Gregory Lupton, Gabrielle Baumberg \\ Supervised by: Dr. Tomasz Kurowski}

@@

@@

@@

\section{Deployment}
The GitHub project \url{https://github.com/Tersect-Browser/Tersect-browser} README provides detailed instructions for setup, dependencies, and deployment. Here, we expand upon these instructions and give a detailed overview of the structure of each extension.

>>>>

% Have put them in alphabetical order
\author{Gabrielle Baumberg, Gregory Lupton, David Oluwasusi, Tanya Stead \\ Supervised by: Dr. Tomasz Kurowski}

@@

The requirements for the application extension were described in [reference Tom’s briefing on this from March]. For the biologist to be able to:

\begin{itemize}
    \item open a genome browser within Tersect Browser and investigate specific variants.
    \item see specific genes of interests against suspected introgressions. 
    \item identify areas where high-impact variants are visible. 
    \item be able to genereate DNA barcodes for the varioius cultivars and species in the dataset. 
    \item to be able to load additional datasets, including for other crops. 
\end{itemize}

The extensions were designed and added by the named authors under the supervision of of Dr Tomasz Kurowski between March and May 2025.

@@

[Insert figure in here]

@@

\section{Deployment}
The GitHub project \url{https://github.com/Tersect-Browser/Tersect-browser} README provides detailed instructions for setup, dependencies, and deployment. This section provides additional information.

%Here, we expand upon these instructions and give a detailed overview of the structure of each extension.
